Fast approximate Bayesian inference for small-area estimation of HIV indicators using the Naomi model

### 2023-05-25 src/docs_paper/paper.Rmd
Add plot of nodes overlaid on NUTS marginals for hypers

```{r echo = FALSE}
options(scipen = 100)

@@

plot0 <- ggplot(ground_truth, aes(x = theta1, y = theta2, z = pdf)) +
  geom_contour(col = multi.utils::cbpalette()[1]) +
  coord_fixed(xlim = c(-2, 4.5), ylim = c(-2, 4.5), ratio = 1) +
  labs(x = "", y = "") +
  theme_minimal() +
  guides(size = FALSE) +
  theme(
    axis.text.x = element_blank(), axis.ticks.x = element_blank(),
    axis.text.y = element_blank(), axis.ticks.y = element_blank()
  )

@@

add_points <- function(plot0, gg) {
  plot0 +
    geom_point(
      data = mvQuad::getNodes(gg) %>%
              as.data.frame() %>%
              mutate(weights = mvQuad::getWeights(gg)),
      aes(x = V1, y = V2, size = weights),
      alpha = 0.8,
      col = multi.utils::cbpalette()[2],
      inherit.aes = FALSE
    ) +
    scale_size_continuous(range = c(1, 2))
}

@@

We used a Scree plot to select the number of principal components $s < m$ to keep.
Figure showing Scree plot.
Figure showing approximation to precision matrix.
Figure showing positions of nodes on hyperparameter marginal posteriors as compared with NUTS.

@@

colours <- c("#56B4E9", "#009E73", "#E69F00")

@@

histogram <- ggplot(df_compare, aes(x = samples, fill = method, col = method)) +
  geom_histogram(aes(y = after_stat(density)), alpha = 0.5, position = "identity", bins = 30) +
  theme_minimal() +
  facet_grid(method~.) +
  labs(x = "beta_alpha", y = "Density", fill = "Method") +
  scale_color_manual(values = colours) +
  scale_fill_manual(values = colours) +
  theme(legend.position = "none")

>>>>

```{r echo = FALSE}
colours <- c("#56B4E9", "#009E73", "#E69F00")

options(scipen = 100)

@@

plot0 <- ggplot(ground_truth, aes(x = theta1, y = theta2, z = pdf)) +
  geom_contour(col = "lightgrey") +
  coord_fixed(xlim = c(-2, 4.5), ylim = c(-2, 4.5), ratio = 1) +
  labs(x = "", y = "") +
  theme_minimal() +
  guides(size = FALSE) +
  theme(
    axis.text.x = element_blank(), axis.ticks.x = element_blank(),
    axis.text.y = element_blank(), axis.ticks.y = element_blank()
  )

@@

add_points <- function(plot0, gg) {
  plot0 +
    geom_point(
      data = mvQuad::getNodes(gg) %>%
              as.data.frame() %>%
              mutate(weights = mvQuad::getWeights(gg)),
      aes(x = V1, y = V2, size = weights),
      alpha = 0.8,
      col = "#009E73",
      inherit.aes = FALSE
    ) +
    scale_size_continuous(range = c(1, 2))
}

@@

We used a Scree plot to select the number of principal components $s < m$ to keep.
Figure showing Scree plot.
Figure showing approximation to precision matrix.

Figure \ref{fig:node-posiitons} shows the positions of the generated PCA-AGHQ nodes overlaid onto the hyperparameter marginal posteriors obtained NUTS.

```{r node-positions, fig.cap="PCA-AGHQ node positions (green, rug plot) overlaid onto the hyperparameter marginal posteriors (grey, histogram) for each of the 24 hyperparameters."}
knitr::include_graphics("depends/nodes-samples-comparison.png")
```

@@

@@

histogram <- df_compare %>%
  mutate(method = fct_recode(method, "PCA-AGHQ" = "aghq", "NUTS"= "tmbstan")) %>%
  ggplot(aes(x = samples, fill = method, col = method)) +
  geom_histogram(aes(y = after_stat(density)), alpha = 0.5, position = "identity", bins = 30) +
  theme_minimal() +
  facet_grid(method~.) +
  labs(x = "beta_alpha", y = "Density", fill = "Method") +
  scale_color_manual(values = colours) +
  scale_fill_manual(values = colours) +
  theme(legend.position = "none")
